Pharmaceutical Supply Chain Forecasting by using Machine Learning in Ethiopian Pharmaceutical Supply Services

### 2024-10-09 manuscript/05-conclusion.qmd
modify

# Conclusion {#sec-conclusion}
In this study, we embarked on a comprehensive analysis of pharmaceutical demand forecasting within the Ethiopian 
Pharmaceutical Supply Services (EPSS) context. By leveraging five  years of sales data for 37 key pharmaceutical 
products, we aimed to  enhance the accuracy of demand predictions and consequently  contribute to more effective supply 
chain management. Our findings  underscore the significance of accurate demand forecasting in  optimizing inventory 
levels, resource allocation, and overall supply chain operations.

>>>>

# Conclusion {#sec-conclusion}

In this study, we embarked on a comprehensive analysis of pharmaceutical demand forecasting within the Ethiopian 
Pharmaceutical Supply Services (EPSS) context. By leveraging five  years of sales data for 37 key pharmaceutical 
products, we aimed to  enhance the accuracy of demand predictions and consequently  contribute to more effective supply 
chain management. Our findings  underscore the significance of accurate demand forecasting in  optimizing inventory 
levels, resource allocation, and overall supply chain operations.
